This file is dedicated for the ordinal analysis of SALES (5/4/21)

```{r}

SALES <- read.csv("SALES.csv")
```

#Loading Libraries


```{r}
library(tidyverse) # For data wrangling
library(ggplot2) # for graphing / figures - mostly histograms/ppplots here
library(pastecs) # Needed to run normality tests
library(car) # Needed to run Levene test
library(lsr) # Navarro package for running psychology tests
library(psych) # for key psychology stats
library(effects) # Effects package, needed for the estimated means, includes lower/upper 95% conf limits
library(ggpubr)
library(boot); library(ggm); library(ggplot2); library(Hmisc);
library(polycor)
library(lavaan)
library(dplyr) 
library(tidyr)
options(scipen=99) # This is to indicate how many digits after the decimal, this one is for 2 digits, but can be changed
```


#Intro to SALES survey

Q7-Q14	SE (8 questions)
Q15-Q22	TV (8 questions)
Q23-Q32	MG (8 questions), Question 30 is missing. 
Notes: Questions 26 and 31 are repeated
Questions 24 and 29 are repeated

SALES 2 has no X, and doest not have the total coloumn. 
```{r}
SALES2 <-select(SALES, ID:Q32)
```

```{r}
library(psych)
des <- describe(SALES2)
knitr::kable(des[,c("min", "max", "mean", "median", "skew", "kurtosis")], main = "Data Summary")
```

#Normality asssumptions

```{r}
hist(SALES2)
```

```{r}
hist(SALES$total)
```

```{r}
describe(SALES2)
```


#Pearson correlations

```{r}
pear_cor = cor(SALES2)
cor.plot(pear_cor, numbers=T, upper=FALSE, main = "SALES_Pearson Correlation", show.legend = FALSE)
```


#Polychor correlations

```{r}
SALES2 = select(SALES2, Q07:Q32) #selecting the data for correlations
poly_cor = polychoric(SALES2)
rho = poly_cor$rho
save(rho, file = "polychoric.doc")
### Thresholds/Scaling results
poly_cor$tau
```

Plotting correlations

```{r}
Polychor_plot <- cor.plot(poly_cor$rho, numbers=T, upper=FALSE, main = "SALES_Polychoric Correlation", show.legend = FALSE)
```

Comparing the differneces between the two types of correlations

```{r}
diff = (poly_cor$rho - pear_cor)*((pear_cor>=0)*2-1)

cor.plot(diff, numbers=T, upper=FALSE, diag=FALSE)
```

#Ordinal CFA

```{r}
load("polychoric")
# Scree plot
fa.parallel(rho, n.obs=394, fm="pa", fa="fa", main = "Scree Plot")
```


Polymodel 1 using ML as an estimator
```{r}
poly_model = fa(SALES2, nfactor=5, cor="poly", fm="mle", rotate = "none")
save(poly_model, file = "poly_model_ML.doc")
poly_model$loadings
```
```{r}
sink("polymodel_ML.doc")
print(fa(SALES2, nfactor=5, cor="poly", fm="mle", rotate = "none"))
sink()
```

```{r}
fa.diagram(poly_model2)
```
Polymodel 2 using DWLS as an estimator
```{r}
poly_model2 = fa(SALES2, nfactor=3, cor="poly", fm="ULS", rotate = "none")
save(poly_model, file = "poly_model_DWLS.doc")
poly_model2$loadings
```
Exporting output
```{r}
sink("poly_model_DWLS.doc")
print(fa(SALES2, nfactor=5, cor="poly", fm="ULS", rotate = "none"))
sink()
```


```{r}
sink("poly_model_DWLS_3FAs.doc")
print(fa(SALES2, nfactor=3, cor="poly", fm="ULS", rotate = "none"))
sink()
```

#CFA 

```{r}
latents.model_s <- 'SelfEfficacy =~ Q08 +  Q07 + Q09 + Q10 + Q11 + Q12 + Q13 + Q14
TaskValue =~ Q18 + Q15 + Q16 + Q17 + Q19 + Q20 + Q21 + Q22
MasteryGoals =~ Q24 + Q23 + Q25 + Q26 + Q27 + Q28 + Q29 + Q31 + Q32'
```

Run CFA model

```{r}
SALESfit <- cfa(latents.model_s,data = SALES2, ordered= TRUE, estimator = "DWLS") #ordered = true means that the variables are ordered categoricals
#to view summary of the fit
partable(SALESfit) # to have the summary of parameters converted to a dataframe
vartable(SALESfit) # to have the summary of variables converted to a dataframe
parameterestimates(SALESfit)
summary (SALESfit) #parameterEstimates() includes the estimates, standard errors, z value, p value, and 95% CIs for all model parameters.
```
To see a summary of the tests and esimtates of the model

```{r}
summary(SALESfit,fit.measures = TRUE,standardized=TRUE)
```

SInce the values are categorical, one would need to you’ll want to look at expected vs. observed counts in each level instead of residual correlations. You can get that with lavTables(fit).

```{r}
lavTables(SALESfit)
```


```{r}
cor_table <- residuals(SALESfit, type = "cor")

cor_table[upper.tri(cor_table)] <- NA # erase the upper triangle


kable(cor_table, digits=2) # makes a nice table and rounds everyhing to 2 digits
```



Putting the data into a nice table (using knitR)
```{r}
parameterEstimates(SALESfit, standardized=TRUE) %>% 
  filter(op == "=~") %>% 
  select('Latent Factor'=lhs, Indicator=rhs, B=est, SE=se, Z=z, 'p-value'=pvalue, Beta=std.all) %>%
  kable(digits = 3, format="pandoc", caption="Factor Loadings")
```

```{r}
sink("SALESfit_DWLS.doc")
print(summary(SALESfit,fit.measures = TRUE))
sink()
```


