---
title: "PostQ_Cleaning"
author: "Tamer Said"
date: "18/12/2020"
output: html_document
---

```{r}
postQ <-read.csv("Post Questionnaire.csv")
library(tidyverse)
```

Filter postQ to select only SALES and PostCC

```{r}
postQ <- select(postQ, StartDate ,Q1:SC0)
```

Deleting first 2 rows containing redundant info

```{r}
postQ <- postQ[-c(1,2), ]
```


```{r}
postQ <- rename(postQ, ID=Q1, Picture= Q2, Color= Q3, Gender= Q4, Q07=Q7, Q08 = Q8, Q09 = Q9)
```

Duplicated values 
4250
4268
4272
4279
4281
4293
4294
4310
4368
4381
4408
4419
4419
4538
4538
4571
4571
4739
4739
4755
4755
4756
4756
4760
4760
4765
4765
4899
4899
4907
4907

#Cleaning duplicates (To search for the row that contains the values) use the following command:

#4250
```{r}
which(grepl(4250,postQ$ID))
```
Deleting the one in row 37 since it was not completed

```{r}
postQ <- postQ[-37, ]
```

#4268

One entry will be changed to 4286 instead, the problem with this, is that it will change both values to the same no. i have to select a condition. 

```{r}
if (postQ$ID == "4268" && postQ$Picture == "cat")
+ {postQ$ID <- "4286"}
```



```{r}
which (grepl(4268,postQ$Q1))
```

```{r}

```

