---
title: "PostQ_Cleaning"
author: "Tamer Said"
date: "18/12/2020"
output: html_document
---

<<<<<<< HEAD
Notes on dates

Ms.Rasha group on 16/5

=======
>>>>>>> 958f6d4ed7cb8936b003e4e2c5ff5bd49453f436
```{r}
postQ <-read.csv("Post Questionnaire.csv")
library(tidyverse)
```

Filter postQ to select only SALES and PostCC

```{r}
postQ <- select(postQ, StartDate ,Q1:SC0)
```

Deleting first 2 rows containing redundant info

```{r}
postQ <- postQ[-c(1,2), ]
```


```{r}
postQ <- rename(postQ, ID=Q1, Picture= Q2, Color= Q3, Gender= Q4, Q07=Q7, Q08 = Q8, Q09 = Q9)
```

Duplicated values 
4250
4268
4272
4279
4281
4293
4294
4310
4368
4381
4408
4419
4419
4538
4538
4571
4571
4739
4739
4755
4755
4756
4756
4760
4760
4765
4765
4899
4899
4907
4907

#Cleaning duplicates (To search for the row that contains the values) use the following command:

#4250
```{r}
which(grepl(4250,postQ$ID))
```
Deleting the one in row 37 since it was not completed

```{r}
postQ <- postQ[-37, ]
```

<<<<<<< HEAD
```{r}
write.csv(postQ, 'postQ.csv')

```

I created unique IDs to identify those students with duplicates 

#Loading unique values 
```{r}
postQ <- read.csv("postQ_unique.csv")
```

=======
>>>>>>> 958f6d4ed7cb8936b003e4e2c5ff5bd49453f436
#4268

One entry will be changed to 4286 instead, the problem with this, is that it will change both values to the same no. i have to select a condition. 

```{r}
postQ$ID[postQ$U_ID=="A25"] <- 4286

```
To find the row no., I can use the following command:
```{r}
which (grepl(4268,postQ$Q1))
```

#4272
Change 4272 to 4272A (ALS) on 16/4
```{r}
postQ$ID[postQ$U_ID=="A15"] <- "4272A"
```

#4279. change Female to 4279F

```{r}
postQ$ID[postQ$U_ID=="A133"] <- "4279F"
```

#4281 change Female to 4281F

```{r}
postQ$ID[postQ$U_ID=="A130"] <- "4281F"
```

#4293

```{r}
postQ$ID[postQ$U_ID=="A22"] <- "4293F"
```

#4294



```{r}
which (grepl(4268,postQ$Q1))
```

>>>>>>> 958f6d4ed7cb8936b003e4e2c5ff5bd49453f436
```{r}
postQ$ID[postQ$U_ID=="A23"] <- "4294F"
```

#4310
Change 4310 Ms Rasha to 4310R (16/5)

```{r}
postQ$ID[postQ$U_ID=="A217"] <- "4310R"
```

#4368, change Female to 4368F

```{r}
postQ$ID[postQ$U_ID=="A68"] <- "4368F"
```

#4408, change Female to 4408F
```{r}
postQ$ID[postQ$U_ID=="A98"] <- "4408F"
```

#4419, change male (CES) to "4419C"

```{r}
postQ$ID[postQ$U_ID=="A90"] <- "4419C"
```

#4538, change to 4538F

```{r}
postQ$ID[postQ$U_ID=="A171"] <- "4538F"
```

#4571, The 2 females are in the same session, using IP address, I will add one digit after the 1, to the number. 45710 and 45719. 

```{r}
postQ$ID[postQ$U_ID=="A152"] <- "45710"
postQ$ID[postQ$U_ID=="A162"] <- "45719"
```

#4739, male from bedaya will be changed to 4739B (21/5)

```{r}
postQ$ID[postQ$U_ID=="A241"] <- "4739B"
```

#4755, male from bedaya will be changed to 4755B (21/5)

```{r}
postQ$ID[postQ$U_ID=="A248"] <- "4755B"
```

#4756, male from bedaya will be changed to 4756B (21/5)

```{r}
postQ$ID[postQ$U_ID=="A246"] <- "4756B"
```

#4760, female to 4760F
```{r}
postQ$ID[postQ$U_ID=="A285"] <- "4760F"
```

#4765, female to 4765F

```{r}
postQ$ID[postQ$U_ID=="A302"] <- "4765F"
```

#4899, (16/6) --> 4799

```{r}
postQ$ID[postQ$U_ID=="A335"] <- "4799" 
```
#4907

```{r}
postQ$ID[postQ$U_ID=="A336"] <- "4807" 
```

Correcting a wrong value in gender (From mint to male), color and picture.

```{r}

```

#Saving the changes to csv file

```{r}
write.csv(postQ, 'postQ_unique.csv')
```

#Checking for duplicates on 14/6/21
