---
Title: "SALES Questions"
author: "Tamer Said"
date: "04/08/2020"
output: html_document
---

#Intro to SALES survey

Q7-Q14	SE (8 questions)
Q15-Q22	TV (8 questions)
Q23-Q32	MG (8 questions), Question 30 is missing. 
Notes: Questions 26 and 31 are repeated
Questions 24 and 29 are repeated

There is a missing question: It is important to me that I improve my
science skills.

#Loading Libraries


```{r}
library(tidyverse) # For data wrangling
library(ggplot2) # for graphing / figures - mostly histograms/ppplots here
library(pastecs) # Needed to run normality tests
library(car) # Needed to run Levene test
library(lsr) # Navarro package for running psychology tests
library(psych) # for key psychology stats
library(effects) # Effects package, needed for the estimated means, includes lower/upper 95% conf limits
library(ggpubr)
library(boot); library(ggm); library(ggplot2); library(Hmisc);
library(polycor)
options(scipen=99) # This is to indicate how many digits after the decimal, this one is for 2 digits, but can be changed
```

I created the variable postQ to save it as a variable (data frame) or tibble.
```{r}
postQ <-read.csv("post_unique.csv")
```

To select the columns I am interested in, I want to select the variables that have the SALES questions only (from Q7 to Q32)

Correcting a wrong value in gender (From mint to male), color and picture.

```{r}
SALES[SALES$ID==4468, "Gender"] <- "Male"
SALES[SALES$ID==4468, "Picture"] <- "Buffalo"
SALES[SALES$ID==4468, "Color"] <- "mint"

```


```{r}
SALES <- select(postQ,ID:Gender, Q07:Q32)
```

#Scoring of the SALES Questions

I will use a new code using scale package to see how I could analyze my likert items
```{r}
SALES_pr <- PreProc(SALES) # to pre-process my data
```

Will have to calculate scores into ways: first one is the long format to do my analysis on the questions, then will do a manual modification in excel to change the words into numbers while. The long format does not work well, as each question is repeated 32 times, which bias the score. 

I will not use this option, since it produces many NAs.

```{r}
scoring <- read.csv("scoring.csv")
```


```{r}
SALES_long <- pivot_longer(data = SALES,cols =Q07:Q32,names_to = "Question",values_to = "Response")
```


Joining the tables together to calculate the scores

```{r}
SALES_joined <- inner_join (x = SALES_long, y= scoring, by = "Response")
```

I am not sure why there are lots of NAs, more than those in the excel sheet (original sheet). could it be the case that not all scores are translated.

Finding score of each participant
 
```{r}
SALES_scores <- SALES_long %>% 
             group_by(ID) %>% 
             summarise (SS = sum(Response,na.rm=TRUE))
```

```{r}
describeBy(SALES, group= "Gender")
```

Grouping data by question: I now need to group students' responses by question to do my analysis.

```{r}
SALES_Q <- SALES_joined %>% 
             group_by(Question) %>% 
             summarise (SS = sum(Score))
```

Clearing Response coloumn (6th coloumn)

```{r}
SALES_joined <-SALES_joined[ ,-6 ]
```


#Converting data from long to wide

Joining the tables by ID (trying to change the tables from long format to wide format)
Most of the analysis do not work with the long format and the score is skewed when adding them for partipants. Thus, I need to convert the data back to the wide format using spread function from Tidyr.

```{r}
# The arguments to spread():
# - data: Data object
# - key: Name of column containing the new column names
# - value: Name of column containing values

SALES_wide <- spread(SALES_joined, Question, Score)
```


```{r}
SALES_response <- inner_join (x = SALES_scores, y= SALES_joined, by = "ID")
```


```{r}
describe(SALES_scores, SALES_scores$SS)
```


Max. score is 163 and min. is 1. Median is 56.96, median 58


#Descriptive stats

```{r}
describeBy (SALES_joined, group = "Question")
```


```{r}
describeBy(SALES_Q$SS, group = "Question")
```

```{r}
describeBy(SALES_Q, group = "Gender")
```

```{r}
describeBy(SALES_Q, group = "ID")
```


```{r}
describe(SALES)
summary(SALES)
```
It appears that the data is skewed, the median value is 4.0

#t-test(To see if there is a diff between males and females)

```{r}
SALES_joined[SALES_joined$ID==4468, "Gender"] <- "Male"
```


```{r}
# independent 2-group t-test
# t.test(y~x).. where y is numeric and x is a binary factor

t.test(SALES_joined$Score ~ SALES_joined$Gender)
```

It appears that there is a significance diff. between the groups. 

#Graphs

```{r}
hist(SALES)
```
Frequency of scores

```{r}
hist(SALES_scores$SS)
describe(SALES_scores$SS)
```


It appears that there is a left skew in my data, very few people scored more than 100, while the mean value is 57. The max. possible score is 125.

I would like to check the structure of my variables.

```{r}
str(SALES_joined)
```

To check for missing values
```{r}
is.na(SALES_joined)
```

```{r}
summary(SALES_joined)

```

```{r}
plot <- ggplot() + 
	geom_bar(data = SALES_joined, aes(x= Gender, y= Question, fill = response), stat="identity") +
  
	geom_hline(yintercept = 0, color =c("black")) + 
	scale_fill_manual(values = SALES_joined$Response, 
		breaks = c("Strongly Agree", "Agree", "Not Sure", "Disagree", "Strongly Disagree"),
		labels = c("Strongly Agree", "Agree", "Not Sure", "Disagree", "Strongly Disagree"), +
	
	theme_classic ())
```
The code did not work.

```{r}
write.csv(SALES_scores, "SALES.scores.csv")
```

Checking the stats of the questions


#Boxplots

```{r}
boxplot(Score~Question, data=SALES_joined, main= "SALES Questions ",
   xlab="Question ", ylab="Score")

#Note that you put y-axis(score), then x-axis(question)
```
Probably the numbers are biased, because each question is counted more than once because of the changed data format.

```{r}
boxplot(Score~Question, data=SALES_Q, main= "SALES Questions ",
   xlab="Question ", ylab="Score")

```

```{r}
boxplot(Response ~ Gender, SALES_long)

```

#Histograms

```{r}
hist_score <- hist(SALES_joined$Score)
```


```{r}
ggbarplot(SALES_joined, x = "Question", y = "Score",
          fill = "Score", sort.by.groups = TRUE)
```

#Notes on normality, it looks that the scores are not normally distributed.

```{r}
SALES_hist <- ggplot(SALES_joined, aes(Score)) + 
geom_histogram(aes(y = ..density..), colour = "black", fill = "white") +
labs(x = "Question", y = "Score")

SALES_hist + stat_function(fun = dnorm, args = list(mean = mean(SALES_Q$Score,
na.rm = TRUE), sd = sd(SALES_Q$score, na.rm = TRUE)), colour = "black", size = 1)
```


```{r}
describeBy(SALES_Q$Score, group = "Question")
```

#Correlations

Running correlations for the whole data frame. This command below excludes the missing values and those that are not numeric.
```{r}
cor(SALES[sapply(SALES, is.numeric)], use='pairwise')
```


Saving the correlation matrix to data

```{r}
SALEScorr <- cor(SALES[sapply(SALES, is.numeric)], use='pairwise')
```
#Barlette test on the correlation matrix in prep for FA. The p value shall be less than 0.5.
A significant test tells us that the R-matrix is not an identity matrix (identity matrix is the case when variables are NOT related to each other and corr is zero); Therefore, if it is significant then it means that the correlations between variables are (overall) significantly different from zero, if Bartlett’s test is significant then it is good news (Field, 2009)
```{r}
cortest.bartlett(SALEScorr, n=394)
```
$chisq
[1] 5277.438

$p.value
[1] 0

$df
[1] 300

#KMO test for the degree of common variance (ideally, a score of 0.5 or higher is good). values close to 1 indicates that patterns of correlations are relatively compact and so factor analysis should yield distinct and reliable factors.

```{r}
KMO(SALEScorr)

```
Overall MSA =  0.95

Saving correlation df as a matrix

```{r}
SALESMatrix <- as.matrix(SALEScorr)
```

#leven's test

```{r}
leveneTest(SALES_Q$Question, SALES_Q$SS)
```

#Factor Analysis

Loading libraries

```{r}
library(tidyverse) # For data wrangling
library(lavaan) # For CFA/MI/SEM
library(semPlot) # For CFA/MI/SEM
library (semTools) # For CFA/MI/SEM
library(OpenMx) # For SEM
library(pastecs) # Needed to run normatlity tests
library(car) # Needed to run Levene test
library(lsr) # Navarro package for running psychology tests
library(psych) # for key psychology stats
library(effects) # Effects package, needed for the estimated means, includses lower/upper 95% conf limits
options(scipen=99) # This is to indicate how many digits after the decimal, this one is for 2 digits, but can be changed
```
CFA and 1-defining the model

Q7-Q14	SE (8 questions)
Q15-Q22	TV (8 questions)
Q23-Q32	MG (9 questions) #Question 30 is not present in the survey

Let's start be defining the measurement model

```{r}
latents.model <- 'SelfEfficacy =~ Q08 +  Q07 + Q09 + Q10 + Q11 + Q12 + Q13 + Q14
TaskValue =~ Q18 + Q15 + Q16 + Q17 + Q19 + Q20 + Q21 + Q22
MasteryGoals =~ Q24 + Q23 + Q25 + Q26 + Q27 + Q28 + Q29 + Q31 + Q32'
```

Run CFA model


```{r}
SALESfit <- cfa(latents.model, data = SALES)#stardard fit
summary(SALESfit) #to view summary of the fit
partable(SALESfit) # to have the summary of parameters converted to a dataframe
vartable(SALESfit) # to have the summary of variables converted to a dataframe
parameterestimates(SALESfit) #parameterEstimates() includes the estimates, standard errors, z value, p value, and 95% CIs for all model parameters.
```
To see a summary of the tests and esimtates of the model

```{r}
summary(SALESfit,fit.measures = TRUE)
```
#Notes reagarding fit measures

Comparative Fit Index (CFI)                    0.848
Tucker-Lewis Index (TLI)                       0.832
RMSEA                                          0.082

#Plotting a sem diagram

```{r}
semPaths(SALESfit, title= FALSE, curvePivot= TRUE)
```
Another way of viewing the plot

```{r}
semPaths(SALESfit, "std", edge.label.cex=0.5, 
         curvePivot = TRUE, exoVar = FALSE)
```

Note: the thicker the lines, the higher the loadings. 

#Factor scores (refer to https://rdrr.io/cran/lavaan/man/lavPredict.html)

```{r}
fit <- cfa(latents.model, data = SALES, se = "robust", test = "Satorra-Bentler") 
head(lavPredict(fit)) #first we need to define the model
head(lavPredict(fit, type = "ov")) #then we use the lavpredict function to compute estimated values for latent variables.
idx <- lavInspect(fit, "case.idx") #The lavInspect() functions can be used to inspect/extract information that is stored inside (or can be computed from) a fitted lavaan object. 
SALESfscores <- lavPredict(fit, newdata = SALES)
## loop over factors
for(fs in colnames(fscores)) {
SALES[idx, fs] <- fscores[ , fs]
} #I am not sure what does the last piece of code mean.
head(SALES)
summary(SALESfscores)
```
#Question:  By checking the idx cases, only 365 cases out of 395 were considered. I am not sure why was that the case. 

Converting fscores from lavaan matrix to dataframe
```{r}
SALESfscores.df <- as.data.frame(SALESfscores)
```

Saving SALES scores in a new file

```{r}
write.csv(SALESfscores.df, "SALESfscores.csv")
```

#Matching the scores with the cases. To do so,I had to create row nos. in both cases to match them. 

Add new coloumn to existing df (idx) row no. to identify the cases
```{r}
SALESfscores.df$rowno = idx
```
Creating a new coloumn for row no. in the SALES 

```{r}
SALES$rowno = seq.int(nrow(SALES))
```

```{r}
SALESfscore_joined <- inner_join (x = SALES, y= SALESfscores.df, by = "rowno")
SALESfscore_joined

```

```{r}
SALES_Factors <- select(SALESfscore_joined,ID:Gender, SelfEfficacy:MasteryGoals)
```

Saving salesfacotrs to a new  file 
```{r}
write.csv(SALES_Factors, "SALES_Factors.csv")
```

#Checking normality of the fscores

```{r}
hist(SALESfscores.df)
```
#Adding normality curve

```{r}

SALESF_hist + stat_function(fun = dnorm, args = list(mean = mean(PALS$sum,
na.rm = TRUE), sd = sd(PALS_Q$score, na.rm = TRUE)), colour = "black", size = 1)
```




