---
Title: "SALES Questions"
author: "Tamer Said"
date: "04/08/2020"
output: html_document
---
I created the variable postQ to save it as a variable (data frame) or tibble
```{r}
postQ <-read.csv("Post Questionnaire.csv")
```
I used the summary function to have a quick look over my data 
```{r}
Summary(postQ)
```

i have to load tidyverse package first
```{r}
library(tidyverse)

```

To select the coloumns I am interested in, I want to select the variables that have the SALES questions only (from Q7 to Q32)

```{r}
SALES <- select(postQ,Q1:Q4, Q7:Q32)
```
To delete the row no. 2 inserted by qualitrics by mistake ( the 2 indicate the row number)

```{r}
SALES <- SALES[-2, ] 
```

I am going to rename the variables instead of having question names

```{r}
SALES %>% 
  rename(ID= Q1, Picture= Q2, Color= Q3, Gender= Q4)
```

Scoring of the SALES Questions

```{r}
scoring <- read.csv("scoring.csv")
```

Arranging data in long format ( I got confused here, and converted the whole dataset rather than SALES, is there a way to undo this?)

```{r}
postQ_long <- pivot_longer(data = postQ,cols =Q7:Q32,names_to = "Question",values_to = "Response"  )
```

```{r}
SALES_long <- pivot_longer(data = SALES,cols =Q7:Q32,names_to = "Question",values_to = "Response"  )

```
Renaming variables in SALES_long

```{r}
SALES_long %>% 
  rename(ID= Q1, Picture= Q2, Color= Q3, Gender= Q4)
```

Joining the tables together to calculate the scores

```{r}
SALES_joined <- inner_join (x = SALES_long,y= scoring, by = "Response")
```

Renaming the columns
 
```{r}
SALES_joined %>% 
  rename(ID= Q1, Picture= Q2, Color= Q3, Gender= Q4)
```
Finding score of each participant
 
```{r}
SALES_scores <- SALES_joined %>% 
             group_by(Q1) %>% 
             summarise (SS = sum(score))
```
I would like to check the structure of my variables
```{r}
str(SALES_joined)

```

To check for missing values
```{r}
is.na(SALES_joined)
```
```{r}
summary(SALES_joined)
```

```{r}
SALES_joined %%
  rename(ID= Q1, Picture= Q2, Color= Q3, Gender= Q4)
```

