---
Title: "LEARNING"
author: "Tamer Said"
date: "16/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

I created the variable postQ to save it as a variable (data frame) or tibble
```{r}
postQ <-read.csv("Post Questionnaire.csv")
```

Load tidyverse library

```{r}
install.packages("tidyverse")
```
Load tidyverse library
```{r}
library(tidyverse)
```

I used the summary function to have a quick look over my data 
```{r}
Summary(postQ)
```

I forgot to add the ID no. and picture, so I added them here, 

```{r}
SALES <- select(postQ,Q1:Q4, Q7:Q32)
```


```
I am going to rename the variables instead of having question names

```{r}
SALES %>% 
  rename(ID= Q1, Picture= Q2, Color= Q3, Gender= Q4)
```

Scoring of the SALES Questions

```{r}
scoring <- read.csv("scoring.csv")
```

Arranging data in long format ( I got confused here, and converted the whole dataset rather than SALES, is there a way to undo this?)

```{r}
postQ_long <- pivot_longer(data = postQ,cols =Q7:Q32,names_to = "Question",values_to = "Response"  )
```

Now I am going to arrange the SALES reponses in long format (check with Michelle if what I got looks correct)

```{r}
SALES_long <- pivot_longer(data = SALES,cols =Q7:Q32,names_to = "Question",values_to = "Response"  )

```
Renaming variables in SALES_long

```{r}
SALES_long %>% 
  rename(ID= Q1, Picture= Q2, Color= Q3, Gender= Q4)
```
```
Joining the tables together to calculate the scores

```{r}
SALES_joined <- inner_join (x = SALES_long,y= scoring, by = "Response")
```
 Renaming the coloumns
 
```{r}
SALES_joined %>% 
  rename(ID= Q1, Picture= Q2, Color= Q3, Gender= Q4)

```
 
 Finding score of each participant
 
```{r}
SALES_scores <- SALES_joined %>% 
             group_by(ID) %>% 
             summarise (SS = sum(score))
```

