---
title: "Post CC"
author: "Tamer Said"
date: "04/08/2020"
output: html_document
---



To load the library
```{r}
library(tidyverse)
```

```{r}
postQ <- read.csv("Post Questionnaire.csv")
```


To select the variables for the postCC (SC) represents the score)
```{r}
PostCC <- select(postQ, Q1:Q4,SC0)
```

To delete the 2nd row 
```{r}
PostCC <- PostCC[-2,]
```



To rename the variables, you do not have to use the pipes, but in this case you will have to indicate the name of the dataset

```{r}
PostCC%>% 
  rename(ID= Q1, Picture= Q2, Color= Q3, Gender= Q4, Score=SC0)
```
The command below will remove the missing values implicitly 
```{r}
PostCC <- filter(PostCC, Q1>1)
```
To arrange the data according to ID 
```{r}
arrange(PostCC, Q1)
```
Let's try to arrange the result accorind to score

```{r}
arrange(PostCC, SC0)
```

From this arrangement, it appeared that some students have not filled the questionnaire, so I need to arrange the scores accordingly, and remove those without scores:I created the variable PostCC-Clean

```{r}
PostCC_Clean<- filter(PostCC, SC0 >=0)
PostCC_Clean
```
This code retrieved all the values that are greated than 1 and stored them in the variable PostCC_Clean. Let's check of there are still any missing values in SC0.

```{r}
filter(PostCC_Clean, !is.na(SC0))

```

This command resulted in the deletion of 6 observation, in which the score was missing. 

Renaming the variables

```{r}
PostCC_Clean <- rename(PostCC, ID=Q1, Picture= Q2, Color= Q3, PostCCScore= SC0)

```

lets print
```{r}
head(PostCC_Clean)
```

Again the cleaned variables were not saved, since I did not save the filter command in a new variable. I have to create a new one

```{r}
PostCC_Clean <- filter(PostCC_Clean, !is.na(PostCCScore))
PostCC_Clean
```
to check if there are still any missing values, I will arrange the values by score

```{r}
arrange(PostCC_Clean, PostCCScore)
```

There are still some missing values, I am not sure why they were not removed. 

```{r}
PostCC_Clean <- filter(PostCC, !is.na(SC0))

```

Still not working, wil try anohter one

```{r}
PostCC_Clean<- filter(PostCC, SC0 >=0)
```

This worked!! and 6 variables were removed.. let's check

Now, I need to arrange the rows according to IDs..

```{r}
PostCC_Clean <- arrange(PostCC, Q1)
```

When I ran this command, the missing values returned again. 

I am not sure, if I need to create a new variable to arrange the variables 

I will try to use the pipes to see where the problem is

```{r}
PostCC_Clean <- PostCC  %>%
  filter( SC0 >=0) %>%
  arrange(Q1)

```
Now it worked, the missing data were removed, then the data were arranged according to ID, I will now rename the variables.

```{r}
PostCC_Clean <- PostCC  %>%
  filter( SC0 >=0) %>%
  arrange(Q1 )%>%
  rename(ID= Q1, Picture =Q2, Color = Q3,Gender =Q4, PostCCScore = SC0)

```

```{r}
PostCC_Clean
```
Before merging the data, I need to make sure that there is a common coloumn that has the same name: ID

```{r}
SALES_scores <- rename(SALES_scores,ID= Q1)
```

Merge Data

In this section, I will merge the data from PostCC and SALES to see if there is any coorelation between PostCCScore and SALES score.

I will use the merge command to do so, based on ID. 

```{r}
CC_SALES <- merge(PostCC_Clean,SALES_scores,by = "ID")
```

As we can see i have got 392 observations, 6 variables 


Is it possible to merge by more than one critieria? I am going to try that

```{r}
CC_SALES <- merge(PostCC_Clean,SALES_scores,by = "ID", "Picture")
```

This did not work, since the SALES-Scores does not have picture, it's only ID.

```{r}
CC_SALES <- merge(PostCC_Clean,SALES_scores,by = "ID")
```

I want to try to filter all the NAs from postCC score inorder to convert it to a numeric variable


```{r}
filter(CC_SALES, !is.na(PostCCScore))
```

```{r}
CC_SALES <- filter(CC_SALES, !is.na(PostCCScore))
```

Converting PostCCSCore to numeric in order to do the correlations

```{r}
as.numeric(CC_SALES$PostCCScore)
```
New clean variable
```{r}
CC_SALESClean <- filter(CC_SALES, !is.na(PostCCScore))

```

There are still some variables that I do not want.. Will use another command to filter those unwanted ones. SOme ID numbers are not logical (ex. 8...), in this case, I need to select those ones since the filter command outputs a logical vector (True and false)

```{r}
CC_SALESClean <-CC_SALESClean[-393,]
```

```{r}
CC_SALESClean <-CC_SALESClean[-392,]
```

```{r}
CC_SALESClean <-CC_SALESClean[-391,]
```

```{r}
str(CC_SALESClean)
```

still , the postCCscore is character.. will try to convert it as integer.

Here I will refer to Andy field to see how I can change the variable from character to integer..
Loading packages from Andy field

```{r}
install.packages("Hmisc"); install.packages("ggm");
install.packages("ggplot2"); install.packages("polycor")
```

Converting PostCCScore to integer

```{r}
CC_SALES %>%
PostCCScore <- as.numeric(PostCCScore)
```

I kept getting an error message using the code above, so I had to create a new variable PoCC that is a numeric vector

```{r}
PoCC <- as.numeric(CC_SALES$PostCCScore)
```

Correlation test

```{r}
cor.test( CC_SALES$SS,PoCC)
```


PLOTS

I will start to do some plotting to see if there are any relationship between the scores

before doing a plot, we need to check the summary of the data using summary command

```{r}
summary(CC_SALES$SS)
```

Let's try a box plot to see the distribution of the Sales score

```{r}
boxplot(CC_SALES$SS, col = "blue")
```
Let's try the same for PostCC score

```{r}
boxplot(PoCC, col = "blue")
```
Histogram
```{r}
hist(CC_SALES$SS)
```

After seeing the plots, it appears that there are some outliers (over 200), since the maximum score is 125 (25*5), maybe some students have done the survey twice, which could skew the data.. I will create a new varaible and include only the ones less than or equal 125

```{r}
SSNew <- filter(CC_SALES, SS <= 125)
```

This command rendered 353 observations instead of 375..

Will try a scatter plot now and see if the relation changes after removing the outliers

```{r}
hist(SSNew$SS)
```
After removing the outliers, we can see that the Sales score is normally distrubuted, but is left skewed.

Let's see the scatter plot between the new SS and Post CC


```{r}
mygraph <- ggplot(CC_SALESClean, aes(SS, PostCCScore))
```
Now, I will specify the figure to be shown , e.x.point
```{r}
 mygraph + geom_point()
```

We can change the size of the point here

```{r}
mygraph + geom_point(size = .5)
```
This graphs allows for a boxplot that shows the difference bet gender in the sales score

```{r}
 boxplot(SS ~ Gender, CC_SALES)
```


```{r}
mygraph + geom_point(aes(colour = Gender))
```

#My work on 26/5/2021

libraries

```{r}
library(ltm)
library(mirt)
library(tidyverse)
library(polycor)
library(lavaan)
library(dplyr) 
library(tidyr)
library(psych)
library(mirt)
library(ltm)
library(ggpubr)
library(SmartEDA)
```


```{r}
PostQ <- read.csv("postQ_unique.csv")
```

```{r}
PostCC <- select(PostQ, ID, Q35:Q51)
```

```{r}
write.csv(PostCC, "PostCC.csv")
```


coonverting IDs to factors

```{r}
PostCC$ID <- factor(PostCC$ID)
```

#Replacing blank values with "NAs"
I discovered some blank responses, and I need to replace them by NAs (since the system recongize them as not blank or not missing)

```{r}
PostCC <- read.csv("PostCC.csv",header = T, na.strings=c(""," ","NA"))
```


Replacing NAs (for now, I will replace them, later I can do multiple imputations). I noticed that Q23 has only 20 responses. I will deselect it for now. Q7 is a qualitative question, so it will be deseclted for now.

#Renaming variables: I need to rename the questions to the same names as the pre in order to refer to do the comparative analysis.

```{r}
 PostCC <- rename(PostCC, Q08post=Q35, Q09post= Q36, Q10post= Q37, Q11post= Q38, Q12post = Q39, Q13post= Q40, Q14post = Q41, Q15post = Q42, Q16post= Q43, Q17post = Q44, Q18post = Q45, Q19post = Q46, Q20post = Q47, Q21post = Q48, Q22post = Q49, Q24post = Q51)
```



```{r}
PostCC <- select (PostCC, ID:Q24post)
```


```{r}
write.csv(PostCC, "PostCC.csv")
```

Converting data to long format

```{r}
PostCC_long <- gather(PostCC, Question, Response, Q08post:Q24post, factor_key=TRUE)
```

```{r}
PostCC_long %>%
select(ID:Response)
```
Descriptive analysis: Frequency analysis
```{r}
PostCC_Frequency <- ExpCustomStat(PostCC,Cvar = c("Q08post","Q09post","Q10post", "Q11post", "Q12post", "Q13post", "Q14post", "Q15post", "Q16post", "Q17post", "Q18post", "Q19post", "Q20post", "Q21post", "Q22post", "Q24post"), gpby= FALSE)
```

```{r}
write.csv(PostCC_Frequency, "PostCC_Frequencies.csv")
```

```{r}
scoring <- read.csv("scoring_CCcopy.csv")
```

```{r}
scoring2 <- read.csv("Scoring_CC2_copy.csv")
```

```{r}
PostCCscores2 <- inner_join(PostCC_long, scoring2, c("Response"))
```

Exporting the PostCC scores

```{r}
write.csv(PostCCscores2, "PostCCscores.csv")
```

```{r}
PreCCscores <- read.csv("PreCCscores.csv")
```

#Joining the pre and post tables

```{r}
PrePostCC <- inner_join(PreCCscores, PostCCscores2, c("ID"))
```

The table produced a giant data frame (84k observations) since each question was labeled twice, and the data was not named correctly. Wil now use the same labels for both questions.

```{r}
PostCC2 <- select(PostQ, ID, Q35:Q51)
```


```{r}
PostCC2 <- rename(PostCC2, Q08=Q35, Q09= Q36, Q10= Q37, Q11= Q38, Q12 = Q39, Q13= Q40, Q14 = Q41, Q15 = Q42, Q16= Q43, Q17 = Q44, Q18 = Q45, Q19 = Q46, Q20 = Q47, Q21 = Q48, Q22= Q49, Q24 = Q51)
```

```{r}
PostCC_long2 <- gather(PostCC2, Question, Response, Q08:Q24, factor_key=TRUE)
```

```{r}
PostCCscores2 <- inner_join(PostCC_long2, scoring2, c("Response"))
```

```{r}
PostCCscores2 <- PostCCscores2 %>% 
  rename(PostValue= value) %>% 
  select(ID:PostValue)
```

```{r}
write.csv(PostCCscores2, "PostCCscores2.csv")
```

```{r}
PreCCscores <- rename(PreCCscores,PreValue= value ) %>% 

PreCCscores <- select(PreCCscores, ID:PreValue)
```

